It was 1825. The carriage jounced over Sheffield's cobbles, its springs protesting like a tormented soul with every rut. Yiming Yael braced himself against the squab, the damp wool of his Oxford trousers clinging to his thighs. Through the rain-streaked window, the city emerged - a beast of brick and iron, its hide crusted with grime. Gas lamps flickered in the murk; their haloes smeared by soot-flecked rain. The stench seeped through the cracks: sulphur and scorched metal, the reek of a thousand privies stewing in factory effluent. Oxford's quadrangles, with their honeyed stone and prim herb gardens, might as well have been on the moon.

His father's house squatted at Church Street's end; its Georgian symmetry marred by the tumorous growth of the Yael Steelworks. Twin chimneys vomited black smoke; their brick throats scarred by decades of heat. The East Works' steam hammer thudded a migraine rhythm - ka-doom, ka-doom - each blow vibrating through Yiming's teeth. His hands clenched, remembering the blistering heft of a puddling rod, the way molten steel shimmered like Satan's honey. A year of handling pipettes and gilt-edged textbooks hadn't calloused his palms, but the ghosts of sparks still danced behind his eyelids.

`Mind your step, sir.' The coachman offered a grimy hand as they halted. Yiming's boots sank into the clart, the mud sucking greedily at his soles. A movement caught his eye - a flash of auburn in the Saltz attic window, there and gone. Cupric. Her family's two-up-two-down leant against the cooperage like a drunkard, its windows patched with newsprint. A year since he'd last seen her, since she'd spat `traitor' at his heels as the Oxford coach pulled away.

The door creaked open before he could knock. Penelope Yael stood in the vestibule, her lace cap askew, flour dusting her cuffs. `Yiming!' She crushed him to her bosom, the scent of yeast and lavender water cloying. Her fingers, brittle as kindling, traced his cheekbones. `You're all angles now. Don't they feed you between those experiments?'

`Enough mollycoddling, woman.' Duncan Yael's voice rolled from the parlour, where he stood silhouetted against the fire's blaze. A ledger dangled from one hand, its pages swollen with figures; the other gripped a meerschaum pipe, its bowl glowing like a Cyclops' eye. `Well? Did they school you in turning virtue to vice, or is Oxford still peddling fairy stories?'

Yiming set his trunk down carefully, its brass fittings catching the firelight. `Metallurgy has come on since your day, Father. Bessemer's converter can produce steel in minutes, not days\dots'

`Bessemer?' Duncan's laugh boomed off the wainscoting. `Aye, I've heard of his toy. Brittle as a whore's promise. Proper steel needs a puddle's sweat, a furnace's heart.' He jabbed the pipe toward the window, where the East Works belched its eternal breath. `That's real. That's legacy.'

Penelope clattered the teacup onto its saucer. `The Derby contract is secured,' she interjected, voice quavering. `Two hundred tons of rails for the Midland extension.'

Duncan grunted. `And Cooper's hands shake too much to stir a cuppa. You'll take his shift tomorrow. High time you learnt the cost of that fancy education.'

Yiming's gut tightened. `My research on crystalline structures - the Royal Society has shown interest\dots'

`Research?' Duncan slammed the ledger onto the sideboard, sending a Wedgwood shepherdess teetering. Penelope lunged to steady it. `Your research is here. In the men coughing their lungs into the clinker. The widows queueing at the gates for their pittances.'

The words hung like a shroud. Somewhere in the East Works, a steam whistle screamed.
A commotion erupted outside - a cacophony of shouts and the metallic clang of a shovel struck against iron railings. Yiming parted the parlour's heavy drapes. Below, two dozen grinders clustered at the factory gates, their leather aprons glistening with rain and sweat. At their forefront stood Cupric Saltz, her hair a riot of copper under the gaslight, face smeared with charcoal.

`\dots no more fingers for your ledger!' she was shouting, her Yorkshire vowels sharp as a grinder's wheel. A boy beside her - couldn't have been fifteen - held up a bandaged hand, the cloth stained rust-brown. `You tell Master Yael his machine is a butcher! We down tools till it's hobbled!'

Duncan yanked the curtain from Yiming's grip. `Saltz's brat,' he growled. `Ought to have had her clapped in irons when she unionised the polishers.'

Yiming's throat constricted. Memories ambushed him - Cupric at twelve, daring him to lick frost from the anvils; at fifteen, pressing a smouldering kiss to his mouth behind the coal bunker, her lips tasting of liquorice and defiance. Now she stood like some avenging angel, her father's old rivet hammer slung across her back.
Penelope wrung her hands. `Duncan, perhaps if we hired a machine-minder\dots'

`We're not coddling mollycoddles.' Duncan turned his flint gaze on Yiming. `First shift is at five. See you don't shame the name.'

Midnight found Yiming picking through the allotments behind Church Street, the air reeking of cabbages and coal tar. The Saltz cottage loomed ahead, its lone attic candle guttering. He'd once scaled the drainpipe to that window, smuggling toffees and penny dreadfuls to a giggling Cupric. Now he stood frozen, a sheaf of papers clutched to his chest - detailed schematics for automatic shut-off valves, pressure gauges, everything he'd studied and scribbled through sleepless Oxford nights.

The scullery door screeched. Cupric stepped into the moon wash, arms crossed over her patched bodice. `Lost your way to the manor, Master Yael?'

`I want to help.'

`Help?' She barked a laugh. `Your dad's machines are chewing through us. Young Enid Thompson - got her braid caught in the rollers last week. Scalped her like a sheep.'

Yiming recoiled. `Christ, Cupric - I didn't\dots'

`Course not. You're off scribbling in your la-di-da journals.' Her voice cracked. `Why'd you come back? To play at gentry? To tally the bodies in your dad's ledger?'

He thrust the schematics forward. `The Sheffield Iris will publish these next week. Guarded gears, emergency stops - it's all possible. Safer than your strikes.'
She stared at the papers, her face a mask. Slowly, she reached out - not for the documents, but to grip his wrist. Her palm was rough as a rasp. `You think ink changes anything here? Your dad will burn that tripe, same as he burned the last petition.'

`Then we'll make him choke on it.' Yiming turned her hand over, tracing the scar that laddered her forearm - a childhood mishap with a hot rivet. `The Board of Trade's passing new safety acts. If we document the accidents, get the press\dots'
A shutter banged overhead. Cupric yanked free. `Still spinning castles in air,' she muttered, but her eyes gleamed wet. `Meet me at the coppice Sunday. Bring proof.'

Dawn's first bruise found Yiming in the East Works' belly; the air thick with coke fumes. Men moved like shadows in the hellish glow, their faces swaddled in rags against the heat. Duncan stood at the puddling furnace, sleeves rolled to reveal forearms corded with old burns.

`Watch close,' he growled as a shirtless worker stirred the molten steel, muscles quivering. `This is where men are forged.'

But Yiming's gaze snagged on the details - the boy sweeping clinker, no older than twelve; the grinder coughing pink spittle into his kerchief. And Cupric, feeding sheet steel into the shearing machine's maw, her eyes never leaving the jagged blades.

A scream tore through the din - a steam valve ruptured, scalding vapour engulfing a worker. Cupric lunged, dragging the man clear as the machine's teeth snapped shut on his abandoned crowbar.

Chaos erupted. Duncan bellowed for order, face purpling. Yiming stood paralysed, the worker's blistered flesh imprinted on his vision.

In the ringing silence, Cupric met his gaze across the factory floor. Her lips shaped two silent words: `Prove it.'
The steam hammer resumed its dirge - ka-doom, ka-doom - as Yiming's fingers tightened around the schematics in his pocket. The future loomed, molten and merciless, waiting to be shaped.