The infirmary was a crypt of suffering, its air thick with the cloying sweetness of rot and the sharp bite of carbolic acid. Yiming's shoes stuck to the floorboards, each step pulling like the suck of a swamp as he entered. Mick Brady lay on a splintered oak table, his left hand splayed like a broken starfish. The surgeon, a gaunt spectre with a monocle cracked like a frozen pond, leant over him, tweezers plucking shards of steel from the pulped flesh. Brady's whimpers mingled with the \textit{thump-thump-thump} of the stamping press below, a macabre orchestra conducted by Duncan Yael's iron will.

`Nobbut a scratch,' the surgeon repeated, though his voice trembled as he poured iodine over the wound. The liquid hissed, and Brady's scream tore through the room, echoing off jars of leeches that floated like grotesque raisins. Yiming's stomach churned. A fly buzzed lazily around a bucket of soiled bandages, their rust-brown stains spreading like old maps of suffering.

Cupric's arrival was announced by the creak of floorboards and the scent of defiance. She leant against the doorframe, her silhouette sharp against the grimy window. Her auburn hair, escaping its braid, caught the lamplight like embers. `Still playing the saviour?' she sneered, tossing a crumpled copy of \textit{The Sheffield Iris} onto the table. The headline blared \textit{SAFETY CRUSADER OR CAPITALIST TOOL}? next to a caricature of Yiming clutching a quill while workers burned in a furnace. `Your grand plans made page three - right after a reward for a missing terrier.'

Before Yiming could retort, the stairwell shuddered under heavy footsteps. Duncan Yael filled the doorway, his presence sucking the air from the room. His beard, threaded with iron-grey, bristled as he chuckled, a sound like coal grinding under a boot. `There's my scholar!' he boomed, snatching the broadsheet. His eyes, flinty under bushy brows, scanned the article. `Ventilation ducts? Guardrails? Think we're running a nursery?'

Yiming's jaw tightened. `Men are dying, Father. Brady's hand\dots'

`Brady's hand?' Duncan's laugh curdled. He crumpled the paper and tossed it into an ash-choked hearth, where flames leapt to devour it. `You want to coddle men? Coddle \textit{this}.'

In one fluid motion, he seized Yiming's wrist, his grip vice-like, and slammed his son's palm onto a freshly forged rail propped in the corner. The metal screamed against flesh. Yiming's cry strangled in his throat as the stench of burning skin bloomed - a sickly-sweet odour that mingled with the infirmary's rot. Blisters rose in the rail's serrated pattern, a grotesque brand.

`Pain's the first language here,' Duncan growled, his breath reeking of whisky and burnt almonds. `Learn it, or crawl back to your books.'

When he released him, Yiming stumbled, clutching his hand. Cupric's face was a mask, but her knuckles whitened around the doorframe. Duncan adjusted his paisley waistcoat, its gold watch chain glinting. `Shift starts at five. Don't be late - \textit{Master} Yael.'

Midnight draped Church Street in a shroud of coal dust and silence. Yiming hunched over his desk, the lamplight pooling over schematics of flywheels and pressure valves. His left hand, swaddled in linen, throbbed in time with the distant \textit{clang} of the night shift. The Saltz cottage's attic candle flickered through the fog, a lone star in the smog-choked night.

A pebble \textit{tinkled} against the glass.

Cupric stood in the moonlit garden, her shawl slipping to reveal a collarbone mottled with old burns. She scaled the drainpipe with the ease of a factory cat, boots finding grooves worn by a decade of clandestine climbs. `Well?' she hissed, swinging into the room. Her eyes, green as oxidized copper, flicked to his bandaged hand. `Let's see it.'

He hesitated.

`Christ, Yiming.' She unwound the bandage, her calloused fingers surprisingly gentle. The burn glared up, a raw map of his father's cruelty. From her apron pocket, she produced a tin of salve, its contents reeking of comfrey and resentment. `Old Saltz remedy,' she muttered, smearing it thick. `Kept my dad's stump from rotting after the lathe took his arm.'

Yiming flinched. `The schematics - I've redesigned the shear guards. If we\dots'

`Schematics?' She snapped the tin shut. `Brady's sister came to the union meet. Eight years old, she was. Traded her braid to the barber for a penny.' Cupric's voice cracked. `You know what she asked? If the machines eat hair \textit{and} fingers.'

The air thickened. Somewhere, a nightwatchman's whistle pierced the dark.

Cupric leant in, her breath warm with chicory coffee and fury. `Sunday. The old coppice. Bring proof that ink can bleed.'

She vanished into the night, leaving a charcoal smudge on the sill - and the ghost of a girl who once shared stolen parkin with him behind the dye works.

The East Works' bell tower tolled five, its bronze clapper choked with decades of soot, the sound a leaden dirge that shuddered through the factory's bones. Yiming stood at the edge of the puddling furnace, his branded palm searing inside a sweat-slicked leather glove. Around him, the night shift staggered like revenants, their faces smeared with ash, eyes hollow from fourteen-hour drudgery. The furnace roared, vomiting a cascade of molten steel into moulds with a sound like the devil's own applause. Sparks erupted in a shower of orange stars, singeing Yiming's trousers and stippling the floor with tiny black craters.

`Eyes on the pour, scholar,' barked Joss Cooper, the retiring foreman, his voice a rasp honed by forty years of shouting over machinery. His face was a battlefield - a melted left ear, a scar cleaving his eyebrow like a lightning strike, and a nose flattened by a long-ago tussle with a runaway trolley. He spat a glob of phlegm that sizzled on the furnace's edge. `Daydreamin' gets lads fried. Or worse.' He jerked a thumb toward the shearing shop, where the rhythmic \textit{snick-snick} of blades echoed like a guillotine's promise.

Yiming nodded, his throat too raw to reply. The air tasted of scorched iron and desperation. He'd spent the predawn hours hunched in the clerks' office, copying accident ledgers by guttering candlelight. The pages swam with names and mutilations: \textit{Enid Thompson, 14, scalp degloved by belt drive. Thomas Saltz, 32, arm severed at lathe. Mick Brady, 17, hand}\dots

A whistle shrieked. The men scattered as a crucible tipped, its molten contents sluicing into moulds with a roar that vibrated in Yiming's teeth. Cooper grinned, revealing a black gap where his front teeth had been knocked out by a flying rivet. `Proper science, eh?' he sneered, slapping Yiming's back hard enough to bruise. `None of your Oxford ponce-about.'

Across the floor, Cupric moved through the chaos like a shadow, her hair bound under a scarf frayed at the edges. She fed steel sheets into the shearing machine's jagged maw, her hands a blur. Every third pass, her eyes flicked to Yiming - a flash of green beneath soot-caked lashes. The machine's teeth gnashed, snapping air where her fingers had been half a heartbeat before.

`Yael!' Duncan's voice cut through the din, sharp as a cold chisel. He stood on the gantry above, thumbs hooked in his paisley braces, the gold watch chain at his waist glinting like a serpent's scales. `Up here. Now.'

The iron stairs groaned under Yiming's weight. Duncan leant against the railing, surveying his domain. Below, a boy - barely ten, face smudged with grime - scuttled to collect metal shavings, his hands swaddled in rags gone stiff with old blood.

`See that?' Duncan jabbed his pipe toward the child. The bowl glowed cherry-red, its smoke reeking of cheap shag. `Your \textit{ventilation} nonsense would slow production by half. Men'd starve by winter. Women'd sell their hair for bread.' He turned, his shadow swallowing Yiming whole. `Heard you've been nosing through my ledgers.'

Yiming's gut clenched. `I\dots'

`Think I don't know my own mills?' Duncan's laugh was a bark, his breath a fog of last night's brandy and burnt almonds. `You'll take supper with the Claybournes tonight. Their daughter's fresh from some Swiss finishing school. Pretty little thing, if you ignore the chin.'

`I'm not here to marry into\dots'

`You're here to secure the Derby contract.' Duncan's fingers dug into Yiming's shoulder, blunt nails biting through fabric. `The Claybournes want a scientist son-in-law. You'll smile, nod, and keep your reformist claptrap shut. Or I'll melt your books for scrap.'

The Claybourne mansion loomed over Endcliffe Park, its limestone façade scrubbed raw by servants' lye. Inside, the air stank of beeswax and hypocrisy. Yiming sat stiffly on a Louis XIV chair that threatened to splinter under his factory-stained weight, facing Edith Claybourne - a porcelain doll in lace, her collar climbing her throat like a strangler's vine.

`Papa says you boil metals for sport,' she chirped, her vowels polished to a Mayfair sheen. A footman refilled her wineglass, the claret sloshing like congealed blood. `How perfectly medieval. Do you duel with test tubes as well?'

Across the table, Duncan chuckled into his consommé, the sound a rumble of distant thunder. Yiming's gloved hand throbbed. He'd hidden the copied ledgers under his mattress, wrapped in oilcloth - pages fat with names, dates, the grisly arithmetic of severed limbs.

`Mr Yael?' Edith tilted her head, a canary awaiting song. Her curls bounced, pinned with a ruby brooch that winked like a fresh wound. `Do you waltz?'

A footman slid a plate of venison before him, the meat rare enough to pulse. Yiming's stomach turned. `I\dots haven't had occasion.'

`Oh, but you must!' Her laugh tinkled, brittle as crystal. `Why, only last month, I danced with Viscount Ashley's nephew at Chatsworth. He trod on my toes \textit{twice}.' She leant forward, pearls grazing the tablecloth. `Do you know what he said? That I'm as light as\dots'

The dining room doors burst open.

`Apologies, sir.' A soot-streaked runner tugged his forelock, eyes darting to the silverware. `Accident at East Works. Grinder caught in the rollers.'

Duncan dabbed his lips with a monogrammed napkin. `Which shift?'

`Saltz girl's crew, sir.'

Yiming's chair screeched as he stood. `I'll go.'

`Sit. Down.' Duncan didn't look up from his venison. `Claybourne doesn't pay to watch heroics.

 Midnight clung to the factory like a shroud. Yiming picked through the corpse of the night shift, his lantern hooded to a slit of jaundiced light. The furnaces slept fitfully, their embers glowering like the eyes of a cornered beast. He moved like a thief, past the silent trip hammers and cold rolling mills, toward the clerks' office.

`Three injuries this week,' came a whisper from the shadows.

Cupric leant against a stack of ingots, her face half-lit by the dying forge. She held up a broken gear tooth, its edges jagged as a wolf's fang. `From the shearing machine. Snapped clean during the supper shift.'

Yiming's pulse quickened. `I need the payroll books. To cross-reference injuries with overtime rosters\dots'

`No.' She stepped closer, the reek of machine oil and burnt sugar clinging to her. `You need to \textit{see}.'

She led him through the tooling shop, past dormant presses that loomed like sleeping dragons. In the polishing room, rows of buffing wheels hung silent, their leather straps limp as hanged men. Cupric stopped at a stained workbench, its surface gouged with a thousand frantic scratches.

`Here.' She pressed his branded palm to the wood. His fingers found grooves - dozens of them, shallow and jagged. `Enid Thompson carved these while they stitched her scalp. Says the foreman docked her wages for “damage to equipment”.'

Yiming traced the marks. Letters emerged: \textit{HELP US}.

`Ink bleeds,' Cupric whispered, her breath warm against his ear. `But blood writes louder.'

A boot scuffed stone.

They froze. Down the corridor, a lantern's glow bobbed - one of Duncan's nightwatchmen, his truncheon tapping a jaunty rhythm against his thigh. Cupric shoved Yiming into a storage closet, crowding in after him. Her hipbone dug into his thigh, her heartbeat a wild staccato against his chest.

`Check the offices,' growled the watchman. `Boss says the lad's been sniffing where he shouldn't.'

The shadow paused outside the closet door. Yiming's hand found Cupric's in the dark. Her fingers tightened - not in fear, but fury. Somewhere, a rat skittered over coal dust. The watchman's keys jangled as he moved on.

`Clear,' Cupric breathed, her voice a blade's edge. She shoved the closet door open, moonlight slicing through the factory's grime-streaked windows. `But he'll circle back. Your dad's got more spies than rats in the coke pile.'

Yiming followed her through the labyrinth of idle machinery, their footsteps swallowed by the cavernous dark. The shearing machine loomed ahead, its teeth glinting in the half-light. Cupric snatched the broken gear tooth from her pocket and pressed it into his palm. `Proof,' she said. `That shear's been failing for months. Your dad's too cheap to replace the cogs.'

The metal was cold, its jagged edge biting into his branded flesh. `We need records. Witnesses. The \textit{Iris} won't print hearsay.'

`Witnesses?' Cupric's laugh was bitter. `Ask Edith Claybourne's daddy. His Derby contract is built on our bones.'

Yiming stiffened. The name hung between them like a struck bell. Edith Claybourne - her simpering laugh, her pearls gleaming like a noose.

`You think I want that?' he hissed.

`Don't matter what you \textit{want}.' She turned, the moonlight catching the scar that laddered her forearm. `Your dad's bought you a gilded cage. Question is - you are going to sing in it, or chew through the bars?'

The Claybournes returned at week's end, their carriage clattering into the factory yard like a gilded insult. Edith perched on the seat, her gloved hand fluttering like a wounded dove. `Such a novel atmosphere,' she trilled as Yiming helped her down. `Papa says industry is quite the moral tonic.'

Her father, Reginald Claybourne, strode past without acknowledging the workers hauling coke. His cane - ebony, topped with a silver wolf's head - tapped a martial rhythm. `Yael! Show us this Bessemer nonsense you've been bleating about.'

Duncan materialised, his grin a baring of teeth. `This way, sir. Lad has got a demonstration.'

The Bessemer converter stood in the trial shed, its egg-shaped bulk dwarfing the charcoal furnaces. Yiming's notes trembled in his hands as Edith peered at the apparatus. `Gracious,' she whispered. `It looks like a witch's cauldron.'

`The process removes impurities in minutes,' Yiming began, `reducing costs and\dots'

`Costs?' Claybourne snorted. `My investors aren't schoolmarms. Can it make steel harder?'

`Yes, but the real advantage is\dots'

`Harder steel.' Claybourne nodded to Duncan. `Double the order.'

Edith clapped, her kid gloves muffling the sound to a ghost of applause. `Marvellous! Why, it's like watching a recipe unfold!'

Yiming's throat constricted. Through the shed's open door, he glimpsed Cupric unloading pig iron, her shoulders straining under the weight.

That night, the union gathered in the cooper's yard. Faces flickered in the lantern light - grinders with fingers stubbed by machinery, widows in patched mourning dress. Cupric stood on a barrel, her voice raw. `Yael's lad's got proof. Broken gears. Ledgers. But we need more.'

A woman stepped forward, her shawl slipping to reveal a scalp crosshatched with scars. Enid Thompson. `I'll testify,' she rasped. `They said I leant too close to the rollers. But the belt was frayed - they knew.'

Murmurs rippled. A man held up a hand swaddled in pus-stained linen. `I'll stand.'

`And me.'

`And us.'

Yiming unfolded the schematics, their edges charred from a near-miss with Duncan's pipe. `The Board of Trade meets next month. If we\dots'

A rock shattered the lantern.

`Scab!' someone roared.

The crowd scattered as a brickbat grazed Yiming's temple. Cupric dragged him into the tannery's reeking shadows. `Steady,' she growled, pressing a wad of burlap to his bleeding brow. `Not all trust your pretty words.'

He gripped her wrist. `Do \textit{you}?'

Her eyes flicked to the schematics, then to the blood seeping through the cloth. `I trust actions.'

Duncan's retribution came at dawn. Yiming woke to hammering - not the factory's rhythm, but fists on the door. Two hauliers stood in the gloom, their breath steaming.

`Foreman wants you,' one grunted. `Accident at the converter.'

The trial shed reeked of molten metal and burnt pork. A body lay under a tarpaulin, one boot protruding. Cooper spat. `Idiot leant over the vessel. Got a face full of slag.'

Duncan stared at the corpse, then at Yiming. `Claybourne's here. You'll tell him it were the lad's own fault.'

`It was,' Cooper muttered. `Mason had been drinking.'

`Aye.' Duncan's gaze never left Yiming. `But you'll say it were the machine. That Bessemer's unstable.'

Yiming's stomach turned. `You want me to lie?'

`I want you to choose.' Duncan stepped closer, his voice a saw's edge. `Family. Or traitors.'

Outside, the workers gathered, their silence heavier than any shout. Cupric stood at the front, Enid's scarred scalp gleaming behind her.

Edith Claybourne's carriage rolled into the yard.

The factory yard lay ensnared in a greasy, sulphureous twilight, the sky smothered under a quilt of coal smoke that bled the sun to a jaundiced smear. The air hung thick with the reek of slag - a nauseating cocktail of scorched metal and charred bone - and beneath it, the copper tang of blood seeped into every breath, as if the cobblestones themselves were bleeding. Yiming stood motionless, a marionette with cut strings, caught between his father's iron grip and the seething semicircle of workers. Their faces, etched with soot and decades of swallowed rage, formed a gallery of ghosts: hollow-eyed grinders with fingers gnawed to stumps by machinery, women in threadbare shawls clutching the hands of children already stooped from hauling coke. At the forefront, Cupric stood like a figurehead of defiance, her auburn hair escaping its braid in fiery tendrils, eyes narrowed to slits of emerald fury. Behind her loomed Enid Thompson, her scalp a grotesque tapestry of scar tissue where the rollers had peeled flesh from bone, a living monument to the factory's hunger.

The Claybourne carriage, a lacquered monstrosity emblazoned with a crest of wolves rending wheat sheaves, rattled into the yard with a clatter that seemed to mock the dirge of groaning machinery. Edith Claybourne's gloved hand fluttered at the window, her face a porcelain mask of genteel horror. The carriage's gilt trim caught the feeble light, scattering prisms across the muck - absurd, fleeting rainbows in a world of grime. Her father, Reginald Claybourne, descended first, his wolf-headed cane striking the cobbles with the finality of a headsman's axe. Edith followed, her silk skirts hoisted high as though the very air were contaminated, her gaze skittering over Mason's tarpaulin-shrouded corpse like a bird avoiding carrion.

Duncan's fingers dug into Yiming's elbow, a vise of calloused flesh and simmering wrath. `Choose now,' he hissed, the words slithering into Yiming's ear like oil over flame. `That rabble' - he jerked his chin toward the crowd, where a man with a pinned sleeve spat phlegm onto the stones - `will carve you up for kindling. But family? Family is forged. It endures.' His breath reeked of last night's whisky, sour and combustible, mingling with the pipe smoke that clung to his paisley waistcoat. Across the yard, Reginald Claybourne paused, his polished boots hovering inches from the tarpaulin, his nostrils flaring as if the stench of death were beneath his notice.

Yiming's temple throbbed where the brickbat had struck him, the burlap rag Cupric had pressed to the wound now stiff with dried blood, a crude crown of suffering. The schematics in his satchel - pages of painstaking equations and gear ratios - felt like ash against his hip, their edges curled and blackened from Duncan's pipe. He glanced at Cupric. Her jaw was set, a muscle twitching beneath the soot, but her fingers trembled faintly at her sides, betraying the storm beneath her steel. The workers' murmurs swelled, a wordless growl that vibrated in the marrow, as Enid Thompson stepped forward, her voice a rasping blade. `Tell them, Yael. Tell them how your dad's machines feast on flesh.'

Reginald Claybourne turned, his cane slicing the air. `Yael!' he barked, as though summoning a hound. `This the Bessemer mishap? Your boy's folly?'

Duncan released Yiming's arm, his smile a rictus of feigned contrition. `A tragic lapse, sir. Lad here'll explain.'

The silence that followed was a living thing, thick and suffocating. Somewhere, a steam valve shrieked, a sound like a soul being torn from its moorings. Yiming stared at Mason's boot protruding from the tarp - the leather split at the sole, the sock beneath grey with ingrained coal dust. He thought of Enid's scalp, of Mick Brady's clawed hand, of the grooves HELP US carved into the workbench by trembling fingers. The lie rose in his throat, bitter as coke fumes. `The converter isn't to blame.'

Duncan's smile curdled, his eyes narrowing to slits.

`It was the safety protocols,' Yiming continued, the words ash on his tongue. `The men weren't trained. The gears\dots'

`Liar!' The shout erupted from the crowd - Harris, the grinder with the pinned sleeve, his face a rictus of rage. A clod of mud, plucked from the wheel ruts, arced through the air and struck Yiming's waistcoat with a wet slap, leaving a Rorschach blot of filth.

Edith gasped, her kid gloves flying to her pearls. `Papa, this is unseemly\dots!'

`Enough.' Reginald Claybourne raised his cane, the silver wolf's eyes glinting like malevolent stars. `Yael, your contract dangles by a thread. Control your rabble, or consider our accord void.'

Duncan's face darkened, the veins at his temple pulsing like live wires. He stepped toward Yiming, but Cupric moved faster - a flash of patched skirts and fury. She interposed herself between them, her hands streaked with machine grease, voice raw as a fresh wound. `You want truth? The Bessemer's sound. It's him\dots' she jabbed a finger at Duncan, her nail cracked and blackened - `who'd flay a man alive rather than miss a quota.'

The crowd erupted. A rivet hammer clanged against steel, a tocsin of rebellion. Enid Thompson tore back the tarpaulin, revealing Mason's blistered face - the skin sloughed away in ragged patches, his mouth frozen in a silent scream. Edith retched, stumbling back into the carriage, her silk gloves pressed to her lips. Reginald's composure shattered. `Madness! Yael, you've let rats gnaw your house to splinters!'

Duncan roared, seizing Cupric by the arm, his fingers biting into flesh. `Viper! I'll see you dancing on the gallows\dots'

Yiming moved without thought. His fist connected with his father's jaw, the impact shuddering up his arm like a lightning strike. Duncan staggered, blood welling at his split lip - a crimson bead that traced the furrows of his beard. The yard fell silent, the workers' breath held as one.

Cupric wrenched free, her eyes blazing. `Actions,' she spat, turning to the crowd. `Not words.'

The first brick sailed, striking a haulier's shoulder. The second shattered the Claybourne carriage window, spraying diamond shards across Edith's scream. The workers surged - a tide of rusted tools and decades of swallowed rage. Yiming grabbed Cupric's hand, her calluses scraping against his branded palm, and pulled her toward the trial shed. Behind them, Duncan bellowed orders, his voice drowned by the mob's roar.

Inside the shed, the Bessemer converter loomed - a cold, iron leviathan. Cupric leant against its hull, her chest heaving. `That's your inheritance ash.'

Yiming thrust the schematics into her hands. `Take these to the Iris. Names. Dates. Witnesses.'

`And you?'

He glanced through the doorway - Enid Thompson swung a pry bar at a foreman's knees; Harris grappled a haulier into the mud. `I'll face the Board. With or without him.'

Her fingers brushed his, fleeting as a spark. `Dreamer.'

The word hung in the air as she vanished into the fray. Outside, the factory whistle screamed - a sound like the world tearing at its seams.