The Sheffield Iris struck the cobblestones at dawn, its inky headlines smearing across the wet stone like fresh blood. `YAEL WORKS EXPOSED: BLOOD IN THE STEEL' screamed the front page, the letters jagged as a saw's teeth. Newsboys darted through the factory gates, their voices sharp as rivet guns, hawking copies to workers who clustered in huddles, their breath fogging the October air. Cupric Saltz watched from the shadow of the cooperage, her back pressed to the damp brick, fingers tracing the frayed edge of the newspaper tucked into her bodice. The woodcut of Enid Thompson's scarred scalp stared up from the page, the artist's crosshatching turning her ruined flesh into a grotesque tapestry. Behind her, the East Works loomed, its chimneys belching smoke that stained the dawn the colour of a bruise.

`Saltz!' A foreman erupted from the tooling shop, his face puce beneath a mask of soot and sweat, fists clenched around a truncheon. `You're done. Master Yael says you're not to set foot\dots'

`Already quit.' Cupric peeled her leather apron from her shoulders, the brass buckle clattering to the cobbles like a challenge. The apron, stiff with years of grime and grease, landed at his boots. `Tell your master his machines can kiss my arse.' She turned, the cold air biting through her threadbare shawl, and strode toward the gates. Behind her, the first whispers of rebellion began - a grinder passing the Iris to a puddlier, a boy stashing a copy in the coke pile.

The strike began at noon, not with a roar, but a slow, deliberate unravelling.

Yiming Yael stood in the cavernous vestibule of Sheffield's Town Hall, the chill seeping through his Oxford-tailored coat. The Board of Trade's summons burned in his pocket, its wax seal cracked like the vertebrae of some long-dead creature. Through the leaded windows, he watched Reginald Claybourne's carriage disgorge its occupants onto the steps - Edith first, her kid-gloved hand fluttering like a wounded sparrow as she navigated the icy stones, followed by her father, his wolf-headed cane striking the granite with a sound like gunfire. The carriage's gilt trim caught the weak sunlight, scattering prisms across the soot-stained snow, a fleeting mockery of beauty.

`Mr Yael.' A clerk materialised, his voice as dry as parchment, nostrils flaring at the scent of coal dust clinging to Yiming's hem. `The Board will see you presently.'

The hearing chamber reeked of beeswax and hypocrisy, its oak-panelled walls hung with portraits of dead industrialists. Six men sat at a table polished to a funereal gleam, their faces arranged in varying degrees of disdain. Sir Alastair Thornbury - railway magnate, philanthropist, and owner of three collieries where children still picked slate - leant back in his chair, twirling a monocle. Beside him, Dr. Ezra Hartnell, the Board's `industrial hygienist', scribbled notes with a pen that scratched like a rat's claws. His frock coat, stained yellow at the cuffs, smelled of formaldehyde and moral compromise.

`We've read these\dots allegations.' Thornbury flicked a copy of the Iris with a manicured nail, the newsprint crinkling like dead leaves. `Your own father calls it slander.'

`My father,' Yiming said, the words bitter as quinine, `calls severed limbs incident reports.' He unshouldered his satchel, the ledgers inside thudding onto the table. `Page forty-three. Thomas Saltz, arm severed at the lathe. Page sixty-seven\dots'

Edith Claybourne's gasp cut through the chamber. She perched in the public gallery, her muff pressed to her lips, pearls gleaming like tear tracks. Reginald's hand clamped her wrist, silencing her.

`Irrelevant,' Thornbury drawled. `The Board concerns itself with productivity, not provincial hysterics.'

The East Works ground to a halt at three bells, the machinery's heartbeat stuttering into silence.

It began in the rolling mill - a dozen puddliers `losing' their tongs in perfect synchrony, the molten steel slopping over moulds to hiss and solidify into grotesque slag. Then the grinders' wheels began to `slip', scoring flawless sheets into ruined scribbles. By dusk, the yard thrummed with a new rhythm: the clang of hammers against anvils in deliberate, deafening unison, a coded pulse that rattled the foremen's teeth and sent rats skittering into the drains.

Cupric moved through the crowd like a shadow, her boots silent on the greasy cobbles. `Slow the line,' she hissed to the lathe operators, her breath a pale ghost in the cold. `Break nothing. Bleed him slow.'

Duncan's answer came at twilight, mounted on a black gelding that snorted plumes of vapor into the freezing air. He rode into the yard flanked by hauliers-turned-militia, their truncheons slung like rifles. `Any man not at his post by six,' he bellowed, voice ricocheting off brick, `is sacked and blacklisted. Try the docks with the other rats.'

The hammers faltered. A boy no older than twelve dropped his wrench, eyes wide as shillings. Cupric stepped into the lantern light, her chin lifted. `And who'll make your steel, Master Yael? Your toff friends?' She jerked her chin at the idle Bessemer converter, its cold bulk looming like a sleeping giant. `Heard the Derby line's stalled for want of rails.'

The hammers resumed, louder, the sound a war drum.

Yiming found the Saltz cottage dark, its windows boarded like a corpse's eyelids. A note waited under a chipped milk jug: `Coppice. Midnight.'

He picked through the skeletal trees, frost crunching underfoot, the moon a bone shard in the sky. Cupric stood by the ruins of the old smithy, feeding pages of the Iris to a meagre fire. The flames gnawed at Enid's woodcut, turning her scars to ash. `Your Board's bought,' she said without turning. `Thornbury's wife owns shares in Yael Steel. Hartnell's on your dad's payroll.'

`The hearing's adjourned for evidence.' Yiming crouched by the flames, the ledgers spilling from his satchel. `If we can prove systematic neglect\dots'

`We?' She laughed, the sound hollow as a drained crucible. `Your dad's cut the infirmary. Men are stitching wounds with horsehair. Women are boiling nettles for poultices.'

`Then testify. The Board can subpoena records\dots'

`Board.' She spat into the fire, the spittle hissing. `Same ones who hanged the Luddites. Same ones who'll hang us.'

A twig snapped. They froze.

`Master Yael.' The voice slithered from the dark. Joss Cooper limped into the firelight, his melted ear glistening like candle wax, breath reeking of gin. `Your dad's offering a bounty. Ten quid for the scribbler's name.'

Cupric's hand crept to her belt knife.

`Joss.' Yiming stood slowly, the cold seeping into his bones. `You were Granddad's foreman. You know the old presses - they're deathtraps.'

`Aye.' Cooper's smile showed blackened gums. `And I know which side butters my bread.' He lunged, a rusted shiv flashing.

The fight was brief, brutal. Cupric's knife hilt found his temple with a crack that echoed through the coppice. Cooper crumpled, blood threading through the frost like crimson lace.

`Actions,' she panted, rifling his pockets. A scrap of paper fluttered loose - a shift roster with names circled in grease pencil. Enid Thompson. Harris. Mick Brady's sister. `Snitch list. Your dad's weeding the troublemakers.'

Yiming stared at the names, his breath clouding the ink. `They'll be gone by dawn.'

Cupric tossed the paper into the fire. The flames leapt, hungry. `Best warn them.'

The strikes thickened like clotting blood, the factory district choked under a pall of resentment sharper than November's bite. By week's end, the East Works' chimneys stood cold and skeletal, their usual plumes of coal smoke replaced by a greasy haze from burning rubbish piles. Workers huddled in the shadow of the idle Bessemer converter, passing a dented flask of cheap gin that burned worse than furnace fumes. Their breath hung in spectral clouds, frosting the air as Cupric Saltz moved among them, her voice a low rasp beneath the clatter of hobnailed boots on cobbles. `Slowdowns in the rolling mill,' she instructed, her fingers sketching invisible blueprints in the frosty air. `Jam the trolley tracks with scrap. But keep your heads - no fires, no broken bones. Make it look like rotten luck.'

Rotten luck, it seemed, had taken root in Sheffield like a noxious weed.

Yiming Yael hunched over a battered desk in the cramped back office of the Sheffield Iris, the air thick with the acrid stench of printer's ink and unwashed desperation. The editor, a gaunt spectre named Pickering with ink-stained cuffs and a squint earned from decades of squinting at type, tossed another witness affidavit onto the teetering pile between them. `We'll run the Thompson girl's account tomorrow,' he muttered, lighting a dog-end cigarette with trembling fingers. `But if your father's solicitors slap us with libel\dots'

`Let them.' Yiming massaged his temples, the words of Enid's testimony seared into his mind - the foreman said I leant too close, but the belt was frayed, they knew. Outside, the clang of the Salvation Army's brass bell competed with the raucous shouts of strikers marching past, their voices raw as fresh wounds. `Run it front page. And add this.' He slid a folded note across the desk - a copy of the blacklist, its edges smudged with Cooper's dried blood.

Pickering unfolded it, his sallow face draining to parchment. `Christ, Yael. This'll torch what's left of your family name.'

`Good.' Yiming stared at the peeling wallpaper, its floral pattern blighted by damp. `Burn it all.'

Duncan Yael's retaliation arrived on horseback, swift and brutal as a forge hammer.

Bobbies in navy serge descended on the Saltz cottage at dawn, their truncheons cracking against the warped door like gunshots. `Open up! Sedition charges!'

Inside, Cupric vaulted out the back window, her boots slipping on frost-rimed cobbles still slick from the night's freeze. She vanished into the stinking warren of dye works and tanneries, ducking under lines of sodden cloth that slapped her face like ghostly hands. They found her mother instead - Mavis Saltz, forty-three, rheumatic, and halfway through a pot of weak Darjeeling. They dragged her to Steel Street Station in her nightdress, her moth-eaten slippers slapping the cobbles as neighbours peered through cracked shutters.

`Bastards,' hissed Enid Thompson, clutching a loaf of day-old bread in the bakery queue. The word spread through the picket lines like gangrene, festering in throats already raw from shouting.

By noon, the East Works' gates were barricaded with overturned lorries and heaps of scrap iron, the air vibrating with a new chant: `Free Mavis Saltz! Free Mavis Saltz!'

Edith Claybourne's note arrived on cream vellum, the envelope's flap sealed with a daub of violet wax pressed with her family's crest - two wolves rending a sheaf of wheat. The scent of lily-of-the-valley clung to the paper, cloying and out of place in Yiming's soot-stained lodgings. `Meet me at the Botanical Gardens. 3 o'clock. Urgent. - E.'

He found her by the hothouse orchids, her fur muff trembling like a startled hare in her grip. The glass-paned walls dripped with condensation, the humid air reeking of loam and forced blooms. `Papa's cancelling the contract,' she blurted, her vowels fraying into something almost human. `He says your family's become vulgar. But if you could just\dots apologise to the Board, maybe\dots'

`Apologise?' Yiming stared at her, the orchid petals glistening like raw meat under the gaslight. `For what? Exposing children losing fingers to line your father's pockets?'

Edith's chin quivered, a hairline crack in her porcelain composure. `You used to be civilised. At Oxford, you talked of alloys and\dots and progress.'

`Progress isn't a parlour game.' He turned to leave, his Oxford brogues slipping on the tiled floor.

`Wait!' Her glove caught his sleeve, kid leather soft as a sigh. `There's a meeting. Tonight. At Thornbury's townhouse. They're drafting a statement against the strikes.'

He froze. `Why tell me?'

Her gaze dropped to the orchid beds, where a spider devoured a moth trapped in the petals. `Because you're the only one who didn't laugh when I trod on your toes.'

The Thornbury townhouse blazed with gaslight, its bay windows leaking the clink of crystal and the smug curl of cigar smoke into the frosty night. Yiming lurked in the mews, collar upturned against the reek of horse dung and coal dust, as carriages disgorged Sheffield's elite - mill owners with waxed moustaches dripping with pomade, politicians with gouty limps and watch chains straining across barrel chests. Inside, through a crack in the damask drapes, he glimpsed Duncan pouring brandy for Sir Alastair Thornbury, their laughter sharp as broken glass.

`\dots deploy the militia,' Thornbury was saying, his monocle flashing like a predator's eye. `The Home Secretary's sympathetic. Crush the ringleaders, the rest will scuttle back to their kennels.'

Duncan nodded, swirling his drink, the amber liquid catching the chandelier's glow. `Aye. But the boy\dots'

`Discredit him,' Thornbury purred, stroking his mutton chops. `Say he's unstable. Mad after returning from Oxford, perhaps.'

A hand clamped his shoulder.

`Lost, lad?' A bobby's breath reeked of pickled onions and stale porter.

Yiming bolted, his Oxford shoes slipping on frozen horse dung, Thornbury's laughter chasing him into the inkpot dark.

The militia descended at first light, their boots cracking the ice-sheathed cobbles with a rhythm like rifle fire. They marched in lockstep, truncheons slapping against gloved palms, their breath pluming in the brittle November air. Sunlight glinted off their helmets, polished to a predatory gleam, and the Sheffield crest on their armbands - a crossed hammer and quill, twisted now into a badge of betrayal. At the East Works gates, the strikers stood braced, a ragged phalanx of defiance: women with arms linked like iron chains, men hefting pick handles and broken bricks, children clutching stones slick with morning frost. Cupric Saltz stood atop an overturned lorry, her voice slicing through the frigid dawn like a forge's bellows. `Hold the line!' she roared, her auburn hair escaping its braid in wild tendrils. `They swing a baton, you swing harder! They draw blood, you drown them in it!'

The militia captain, a bull-necked brute with a scar bisecting his left eyebrow like a chalk mark on slate, raised a brass whistle to his lips. The shrill blast tore through the morning, a sound that set the rooks scattering from the factory's eaves.

Chaos unspooled with the inevitability of a snapped cable.

Yiming Yael watched from the sagging roof of the abandoned dye works, his fingers numb around a smuggled police ledger, its pages fluttering like trapped moths in the wind. Below, the picket line buckled under the militia's advance. Truncheons rose and fell in mechanical arcs, the wet thwack of wood on flesh punctuated by screams that curdled the air. Enid Thompson went down first, her scarred scalp splitting anew under a baton's edge, blood pooling black on the frost. Harris lunged at a militiaman, his pinned sleeve flapping like a wounded bird, only to catch a truncheon to the jaw - a crack that echoed off the brickwork.

`Bastards,' Yiming hissed, ink smearing as he scrawled names into the ledger's margins: Sgt. R. Haskins. Pvt. T. Greaves. Cpl. M. Vickers. The ledger trembled in his grip, its pages a damning ledger of bribes - Thornbury's payments to the Chief Constable, neat columns of guineas exchanged for `public order'. Proof. But proof meant nowt if the strikers broke.

A hand seized his collar, yanking him backward.

`Got you, traitor.'

Joss Cooper's replacement - a hulking foreman named Crowe, his face a topographical map of old burns - dragged him toward the roof's edge. Yiming's heels scrabbled on moss-slick slate, the ledger tumbling from his grasp. Pages spiralled into the void below, fluttering like wounded gulls.

`Da says you're to watch,' Crowe growled, forcing Yiming's face toward the carnage. The man's breath reeked of stale ale and boiled cabbage. `Watch what your softness wrought.'

Mavis Saltz's trial lasted seven minutes, a farce performed in the reeking belly of Steel Street Gaol. The magistrate, a prune-faced relic with a hearing trumpet and a wig yellowed by decades of pipe smoke, squinted at the charge sheet through milky eyes. `Sedition\dots conspiracy\dots ah, yes. Possession of incendiary materials.'

`Incendiary materials?' Mavis croaked from the dock, her rheumatic hands trembling on the rail. The gaolhouse stank of urine and despair, the walls weeping condensation. `I've not lit a fire since the Great Exhibition! Me rheumatism won't allow it!'

The prosecutor, a ferret of a man in a threadbare barrister's gown, flourished a charred copy of the Sheffield Iris. `This rag was found in her home, your worship. Filled with treasonous filth.'

Cupric, disguised in a coalman's cap and a face smeared with soot, lurked at the back of the room. Her nails bit crescents into her palms as the gavel fell. `One month hard labour,' the magistrate intoned, already reaching for his snuffbox. `Next case.'

Outside, in the gaol's shadowed alley, she vomited into a gutter, bile and rage steaming in the cold. The taste of failure - sharp as lye - lingered on her tongue.

Edith Claybourne found Yiming at dusk, huddled in the crypt of St. Marie's, the air thick with the scent of damp stone and old mortality. Her fur cloak trailed grave dust as she slipped between the tombs, a wraith in ermine. `They're posting bills,' she whispered, thrusting a leaflet at him. The paper crackled like dead skin. `WANTED: YIMING YAEL - SEDITIOUS ACTIVITY.' His own face stared back, sketched in hasty charcoal, the eyes too wide, the mouth a grimace.

`Why help me?' he demanded, his voice echoing off the crypt's vaulted ceiling. A rat scuttled over a desiccated wreath, its claws clicking like a ticking clock.

She twisted her gloves, the kid leather creaking. `Papa's promised me to Thornbury's nephew. A man who collects taxidermized hounds and\dots and patents.' Her voice frayed at the edges. `You're the only one who didn't bore me.'

He studied her - the chapped lips beneath rouge, the smudged kohl rimming eyes red from weeping. `Can you get to Thornbury's safe?'

`His study's locked.'

`But you're to marry into the family.'

She paled, the crypt's candlelight carving hollows under her cheekbones. `You'd use me?'

`Aye,' he said, no softer than Duncan might. `And you'll let me.'

The safe yielded rotten fruit.

Edith's hands shook as she passed Yiming the documents - shipping manifests for French lace and Portuguese cork, not bribes or blacklists. `It's all trade routes. Nothing about the strikes.'

He cursed, flinging the papers across Thornbury's study. They scattered like leaves, catching the firelight as they fell. `Thornbury's too clever. He'd never keep it here\dots'

Footsteps echoed in the hall, heavy and deliberate.

`Quickly!' Edith shoved him toward the servants' stair, her perfume clashing with the room's cigar-and-leather reek. `If they find you\dots'

`I know.' He hesitated at the door, the weight of her desperation pressing on him like a millstone. `Come with me.'

She glanced at the four-poster bed, canopied in silk the colour of clotted cream, its pillows plump as a banker's purse. `And trade this for a garret? For soup kitchens?'

The door handle turned.

Yiming fled, the taste of betrayal bitter as chicory.

Duncan's trap sprang at midnight, the hour when even the rats grew still.

Crowe and his men dragged Yiming into the East Works' furnace room, its brick walls still radiating the day's phantom heat. Duncan stood before the dormant Bessemer converter, a revolver gleaming in his hand like a surgeon's tool. The furnace door hung open, its maw yawning into darkness.

`Ends here,' Duncan said, pressing the barrel to Yiming's brow. The metal burned cold against his skin. `Either you denounce the strikes at dawn, or you join those in the ground.'

Yiming's gaze flicked to the furnace, and plainly, `You'd kill your own blood?'

`Blood?' Duncan's laugh was a dry cough. `Steel's the only blood that matters.'

The furnace groaned as Crowe stoked the coals, the heat blistering the air.

`Choose.'

The furnace roared to life, its innards glowing a hellish orange as Crowe shovelled coke into the maw. Heat rolled across the room in visible waves, warping the air like a mirage. Yiming's sweat-drenched shirt clung to his back, the revolver's barrel a cold brand against his temple. Duncan's face hovered inches away, his eyes reflecting the flames - two chips of obsidian in a landscape of leathery creases. `Denounce them,' he hissed, spittle sizzling on the furnace's edge. `Stand at the gates at dawn, call them rabble, and the Yael name stays clean.'

Yiming's gaze flicked to the Bessemer converter, its iron flanks streaked with old slag. Actions, not words, Cupric's voice echoed in his skull. He thought of the ledger pages spiralling into the void, of Enid's blood blackening the frost, of Mavis Saltz's gnarled hands gripping the dock. `The Yael name,' he said quietly, `is already ash.'

Duncan's finger whitened on the trigger.

A whistle shrieked outside - not the militia's brass bark, but the factory's own steam horn, wailing like a banshee.

Cupric Saltz stood atop the Bessemer converter, the crowd seething below her like molten ore. She'd pried open the steam valves herself, the horn's cry echoing across Sheffield. Workers streamed into the yard - grinders with bandaged hands, puddliers still clutching their tongs, women from the polishing shops with skirts hitched above their ankles. Even the boys who swept clinker - had come, their faces smudged with soot and resolve.

`They've got Yiming!' she shouted, her voice raw as a fresh wound. `They'll break him, then break us. But we're not stock to be forged!'

A roar surged through the crowd. Enid Thompson, her scalp crusted with dried blood, hefted a crowbar. `Burn it all!'

`Nay.' Cupric's grin was feral. `We'll take it all.'

They surged toward the furnace room, a river of fury and rusted tools.

Edith Claybourne stood in Thornbury's study, the safe gaping like a wound. Her fingers trembled as she sifted through ledgers bound in Moroccan leather. Shipping manifests. Tax records. Letters to the Home Secretary - `My dear.'

She froze. Thornbury filled the doorway, his monocle catching the gaslight. `A curious hour for bookkeeping.'

`I\dots I couldn't sleep.'

`Nor could I.' He stepped closer, his cane's wolf-head snarling. `Odd, how the Yael boy vanished after you visited him.'

Edith's hand closed around a letter opener. `Stay back.'

Thornbury chuckled. `Or what? You'll stab me? Your sort doesn't stoop to vulgarity.'

The blade flashed.

The furnace room door exploded inward, the mob spilling over Crowe's men. Cupric lunged at Duncan, her knife scoring his forearm. The revolver clattered to the floor.

`Finish it!' someone shouted.

Yiming staggered free, the heat blistering his lungs. He locked eyes with Duncan - not a father now, but a cornered beast.

`Do it,' Duncan rasped. `Prove you're my blood.'

Yiming gripped the revolver. The crowd held its breath.

He turned, aimed at the Bessemer converter's steam valve, and fired.

The explosion rocked the East Works. Screeching metal, billowing steam, the groan of iron surrendering to pressure. Workers scattered as the converter listed, its molten guts pouring across the floor in a glowing river.

Duncan howled, lunging for Yiming. Cupric's boot caught his jaw, sending him sprawling into the slag.

`The name's dead,' Yiming said, tossing the revolver into the flames. `Long live the workers.'

The Sheffield Iris hit the cobbles a week later, its headline bold: `YAEL EMPIRE FALLS: STRIKE FORCES REFORMS'.

Edith Claybourne read it in a dockside boarding house, her bandaged hand cradling a mug of bitter tea. The letter opener's thrust had been clumsy, but enough to buy her escape. Outside, gulls wheeled over the trawlers, their cries drowned by the clang of shipbuilders' hammers.

Cupric found Yiming at the coppice smithy, his burned hands binding a new gear for the reforged shearing machines. `Hear they're calling you a hero,' she said.

`Hear they're calling you a terrorist.'

She shrugged. `Same thing, different tongues.'

They worked in silence, the forge's glow painting the dusk. Somewhere, the East Works' whistle blew - not a dirge, but a new rhythm.