The train shuddered out of Sheffield Midland station under a bruise-purple dawn, its whistle drowned by the metallic scream of wheels on tracks. Yiming Yael pressed his forehead to the grimy window, watching the city's jagged silhouette shrink - the East Works' skeletal chimneys, the Saltz cottage's boarded attic, the coppice smithy reduced to a charcoal smudge against the horizon. The compartment reeked of coal dust and stale tobacco, the air thick with the nervous silence of early travellers. Across from him, Cupric Saltz sat rigid, her hands knotted in her lap like twin fists of stone. A copy of the Sheffield Iris lay abandoned on the seat, its headline (`POLICE SEEK STRIKE ``AGITATORS''') half-obscured by her mud-caked boot. Her auburn hair, usually a wild crown, was tucked under a moth-eaten shawl, but her eye - sharp as flint - darted to every creak of the carriage.
`Should've burned that rag,' she muttered, jerking her chin at the paper. Outside, two bobbies patrolled the platform, truncheons swinging like pendulums.
Yiming folded the paper crisply, tucking it into his coat. `Proof we're still newsworthy.' His throat tightened at the sketch below the fold: his face rendered sharper than he remembered, cheekbones like blade-edges, and Cupric's hair a wildfire of ink strokes. The byline hissed with Thornbury's influence: `Dangerous radicals last seen fleeing toward Derby.'
`Derby.' Cupric snorted, picking at a loose thread on her sleeve. `As if we'd be daft enough to leg it north.'
The train lurched, steam hissing like a vengeful spirit as Sheffield's outskirts bled into patchwork fields. Summer sunlight gilded hayricks and grazing sheep, the pastoral calm a mockery of the soot-choked world they'd left. Cupric's nose wrinkled. `Smells wrong.'
`No coke fumes.'
`Aye. Wrong.'
They changed trains at Birmingham New Street, its vaulted iron ribs dripping with decades of soot. The station teemed with porters hauling trunks and hawkers selling meat pies that smelled more of grease than meat. Cupric lingered by a newsstand, her gaze snagging on a fresh stack of Iris papers. `YAEL HEIR STILL AT LARGE', blared the headline.
`Move,' Yiming hissed, steering her into a tea room thick with the reek of burnt toast and gossip. Elderly women in feathered hats sipped Earl Grey, their eyes following Cupric's scuffed boots. Yiming kept his cap low, sanding the Sheffield grit from his tongue. `Two returns to Oxford, please.'
The ticket clerk, a pinched man with ink-stained cuffs, eyed Cupric's frayed shawl. `Visiting the university, are we?'
`Research trip,' Yiming said, sliding coins across the counter. `Metallurgy.'
Cupric's snort was almost convincing. `Aye. Fancy word for staring at rocks.'
The clerk's smirk faded as he stamped the tickets. `Platform three. Mind the gap.'
The Oxford train was a different beast - plush maroon seats, brass fittings polished to a predatory gleam, compartments smelling of lemon oil and unearned privilege. Cupric sank into the upholstery like it might bite, her fingers brushing the antimacassar as if it were spun from spiderwebs. Outside, the Midlands blurred into a watercolour of hedgerows and honey-stone villages.
`How long?' she asked, kicking her boots onto the opposite seat.
`Three hours.'
`Three hours of this?' She flicked a finger at the lace curtain, her voice dripping with mock awe. `Christ, no wonder you turned rebel. I'd gut myself by mile two.'
Yiming's smile felt foreign, a muscle long unused. `Wait until you see the spires.'
`Spires.' She rolled the word like a pebble in her mouth. `That what they call chimneys down here?'
He didn't answer. The train rattled past a churchyard, its headstones tilting toward the tracks like accusing fingers. Somewhere ahead, Oxford waited - a gilded cage he'd once called home.
Oxford in high summer was a symphony of honeyed stone and whispered history, its spires piercing a sky so blue it seemed painted by some celestial artist. The colleges, drowsy with academic slumber, basked in the golden light, their ancient walls cloaked in ivy that rustled like the pages of an unread book. Yiming's garret on Merton Street perched above a cobbled lane where swallows darted and swooped, their wings slicing the air with a precision that made Cupric's fingers twitch for a rivet gun. The room, though cramped, held a certain charm: sunlight filtered through lace curtains (now neatly mended), casting lace-like shadows on a desk strewn with journals, brass callipers, and a microscope polished to a gleam. A faded Persian rug, threadbare at the edges, softened the floorboards, and a cast-iron kettle hissed lazily on the hob, sending curls of steam into the sunbeams.
Cupric stood at the window, her arms folded as though the bucolic scene outside were a personal affront. Below, a milk cart clattered past, glass bottles chiming like discordant bells. `Where's the smoke?' she demanded, nostrils flaring. `The grit? The proper stink of things getting done?'
Yiming glanced up from his valise, where he was unpacking a stack of journals bound in cracked leather. The garret's lone bookshelf sagged under treatises on metallurgy and dog-eared poetry collections, their spines cracked from late-night reading. `No furnaces here,' he said, nodding at the vase of cow parsley wilting on the sill. `Just books. Birds. And botany.'
`Birds,' Cupric repeated, as though diagnosing a moral failing. She jabbed a finger at a swallow perched on a nearby chimney pot. `That one's judging us. Bet it's never worked a day in its life.'
They slipped into a rhythm as foreign and delicate as the hum of a tuning fork. Mornings, Yiming vanished into the Bodleian Library, its cavernous halls smelling of dust, beeswax, and the faintest whisper of mildew. He'd lose himself in journals like Transactions of the Royal Society, tracing Bessemer's early missteps with a pencil clutched like a lifeline. The silence of the reading room was punctuated only by the occasional cough or the rustle of a don's robe, its hem trailing centuries of tradition.
Cupric, meanwhile, claimed the Covered Market as her kingdom. Beneath its vaulted glass roof, stalls groaned under pyramids of strawberries, plump as a vicar's thumbs, and cheese wheels sweating like labourers in the heat. A fishmonger with forearms like hams and a voice like a foghorn taught her to shuck oysters (`Twist the knife, lass - like you're gutting a Tory!'), while a florist with cheeks ruddy as rhubarb gifted her sprigs of rosemary `for luck'. But her favourite conquest was the butcher's stall, where a wiry man in a bloodied apron held court, his cleaver flashing as he dissected cuts of meat with surgical precision.
`Es stultior asino,' she announced one evening, slamming a paper-wrapped pork pie onto the garret's rickety table. The pie's crust flaked ominously, oozing gravy onto a ledger titled The Properties of Wrought Iron.
Yiming nearly dropped his fork. `Where'd you learn that?'
`Butcher's blessing,' she said, sawing into the pie with a pocketknife honed on Sheffield steel. `For good appetite.'
Yiming pinched the bridge of his nose. `It means ``you're dumber than a donkey''.'
Cupric's laughter erupted, bright and unguarded, bouncing off the sloping ceilings. `Reckon he's right. This pork's half gristle.' She flicked a dubious chunk onto the floor, where a bold sparrow promptly claimed it.
For a moment, Sheffield's shadow lifted, replaced by the golden haze of an Oxford dusk filtering through the garret's warped glass.
By week's end, they'd carved out a fragile peace. Cupric mended the lodgings' sagging curtains with a sailor's precision, her stitches as tight as ship rigging. Yiming scribbled notes at a desk groaning under papers, the scratch of his pen harmonising with the coo of wood pigeons nesting in the eaves. Afternoons, they wandered - through Christ Church Meadow, where Cupric scoffed at `posh sheep' nibbling grass trimmed to carpet perfection, and along the Isis, where undergraduates punted with the grace of drunk starlings.
`Could do that,' Cupric said once, watching a punt laden with giggling students veer into the reeds. The pole-wielder, a gangly youth in a boater hat, yelped as his cargo of picnic hampers and champagne flutes teetered precariously.
Yiming raised an eyebrow. `You'd capsize them on principle.'
`Aye,' she grinned, skimming a pebble across the water. Two hops, then a plink. `Reckon I would.' She paused, squinting at the river's shimmering surface. `Though that one's got the right idea.' She nodded at an elderly don gliding past in a punt, his pipe trailing smoke as he read Euripides aloud to a snoozing terrier.
Evenings brought a different magic. They'd clamber onto the garret's sloping roof, a bottle of cider pilfered from the market clutched between them, and watch the bats stitch the twilight. The spires softened into silhouettes, and the air thickened with the scent of lavender from some unseen garden. Below, the lane echoed with the clatter of closing shops and the murmur of students debating Aristotle over pints of bitter.
`Never pictured you here,' Cupric said one night, her voice uncharacteristically quiet. She leant back on her elbows, her boots scuffing the roof tiles. `All this\dots quiet.'
Yiming swirled his cider, the liquid catching the last amber rays of sun. `Never pictured you not swinging a hammer.'
She bumped his shoulder, her calloused fingers brushing his sleeve. `Still could. Your curtains were a right state.'
A silence settled, comfortable as the dusk. Somewhere, a church bell tolled the hour, its resonance lingering in the warm air.
The closest brush with discord came on a Tuesday, when a college porter - a man with a moustache waxed into submission and a bowler hat perched like a nesting bird - mistook Cupric for `a new bedder'.
`Scrub the staircases,' she mimicked in a nasal drawl, storming into the garret with a feather duster clutched like a truncheon. `Handed me this and a bucket! Told him where to stuff his ostrich plume.'
Yiming hid his smile behind a treatise on tensile strength. `They're just unused to\dots'
`To what? Women who don't simper? Women who know a rivet from a rivet gun?'
`To women,' Yiming said, lowering the paper, `who know twelve uses for a rivet.'
She lobbed the duster at his head. It missed, scattering feathers over his notes like misplaced snowfall.
`Thirteen,' she corrected, smirking as she snatched an apple from the fruit bowl. `And if that porter shows his face again, I'll demonstrate number fourteen.'
Oxford's summer draped itself over the city like a silk shawl, languid and sun-warmed, the kind of heat that melted time into a golden syrup. The strikes and sirens of Sheffield felt as distant as a half-remembered dream, their jagged edges softened by honeyed stone and the Isis's gentle currents. Yiming and Cupric, unmoored from the north's turmoil, slipped deeper into the rhythm of their borrowed peace, each day unfolding with the quiet certainty of a well-tempered clock.
Mornings began with the clatter of the milk cart and the trill of blackbirds in the lane below the garret. Yiming, armed with a leather satchel patched with waxed thread and a list of obscure references gleaned from the Bodleian's archives, haunted the library's shadowy stacks. He'd lose hours tracing the lineage of Bessemer's innovations through crumbling journals, his fingers leaving smudges on pages that smelled of vanilla and neglect. One morning, he unearthed a folio of handwritten notes by a 17th-century alchemist - `Observations on the Transmutation of Iron' - its margins littered with sketches of furnaces that resembled pagan altars. The discovery fizzed in his veins like sherbet.
Cupric, meanwhile, struck up an unlikely apprenticeship with the Covered Market's blacksmith-turned-tinsmith, a retired craftsman named Mr. Pevensie. His stall, tucked between a greengrocer's and a haberdashery, overflowed with dented kettles, twisted candlesticks, and a samovar he'd `rescued from a Russian countess' (or so he claimed). His hands, gnarled as old oak roots, moved with the precision of a horologist as he taught her to mend a spout.
`Solder's just liquid rivets,' he'd grunt, squinting through wire-rimmed spectacles. `Same principles. Heat, patience, less swearing.'
Cupric, her sleeves rolled to the elbow, learnt to coax silver seams along cracked seams. `Aye, but rivets don't bite your thumb when you're not looking,' she retorted, sucking a burnt finger.
By noon, they'd reunite at the garret, trading stories over crusty bread and wedges of cheddar so sharp it made their eyes water. Yiming scribbled equations inspired by the Bodleian's alchemist folio, while Cupric tinkered with the samovar, its brass belly dented but defiant.
`Your daft books mention anything about sealing leaks?' she asked one afternoon, blowing a curl of hair from her eyes as solder hissed under her iron.
`Only metaphorical ones,' Yiming said, tossing her a tin of beeswax. `Try this.'
She smeared the wax along the seam, her brow furrowed. `If this works, I'm nominating you for the Royal Society.'
`If it doesn't, I'm blaming the countess.'
Afternoons dissolved into explorations, the city yielding its secrets like a shy lover. They unearthed a tucked-away bookshop on Turl Street, its shelves bowing under esoteric titles and its owner - a former alchemist named Mrs. Thistlewaite - brewing espresso over a Bunsen burner. `Italian madness,' she'd cackle, serving them thimble-sized cups. `Better than ink, eh?'
North of Port Meadow, they found a sun-drenched meadow where gypsy horses grazed, their coats gleaming like polished chestnuts. Cupric, ever pragmatic, befriended the carthorses, feeding them stolen apples and inspecting their shoes for wear. `This one's got a loose nail,' she announced, pointing to a bay mare. `Shoddy work.'
`Not everyone's a Sheffield grinder,' Yiming said, leaning against a lichen-crusted wall.
`Aye, more's the pity.'
They discovered a punt rental shack near Magdalen Bridge, manned by a one-legged veteran named Corporal Briggs. His wooden leg - carved with intricate Celtic knots - thumped against the jetty as he taught Cupric to pole with military precision.
`Straight back, steady grip - like holding a rifle,' he barked, though his eyes crinkled with approval as she navigated the Cherwell's serpentine bends. `You've a knack, lass.'
Yiming, lounging in the punt's bow with a volume of Donne, watched her master the rhythm. The pole dipped, the punt glided, and sunlight fractured on the water like smashed amber. `You're a natural,' he said, dodging a spray of droplets.
`Aye, and you're ballast,' she shot back, splashing him with deliberate aim.
Evenings were reserved for the city's quiet miracles. They attended an open-air production of A Midsummer Night's Dream in New College Garden, Cupric heckling Bottom's ass-head with whispered jabs. `That's you,' she hissed, elbowing Yiming as the actor brayed. `All bookish bray and no bite.'
Another night, they stumbled upon a choir rehearsing in Merton Chapel, their voices rising like incense smoke into the vaulted dark. The harmonies - Byrd's Ave Verum Corpus - turned the stone to liquid. Cupric, uncharacteristically still, traced the stained glass with her eyes. `Never heard owt like that in Sheffield,' she murmured. `Unless you count the foundry whistles.'
Once, they even joined a don's moonlit lecture on celestial navigation in the Radcliffe Square. The don, a stooped figure in a moth-eaten gown, pointed to Orion with a trembling cane. `The hunter's belt aligns with Betelgeuse\dots'
`Stars are just furnaces,' Yiming whispered, tracing constellations with his finger. `Burning hydrogen instead of coke.'
Cupric tipped her flask to the sky. `Bigger than your dad's. And quieter.'
The closest brush with adversity came during a heatwave that clenched the city in a sweaty fist. The garret became a kiln, the air thick enough to slice. Cupric, stripped to her undershirt and breeches, declared war on the heat. She rigged a pulley system from bedsheets to hoist the window higher, jury-rigged a fan from a biscuit tin and salvaged clock springs, and bartered with the milkman for ice chips wrapped in newsprint.
`Sheffield ingenuity,' Yiming said, admiring her contraption. The fan whirred, stirring the soupy air.
`Oxford's softer than a baker's arse,' she retorted, but grinned as the first breeze kissed her neck.
They spent that night on the roof, the cobbles below radiating stored heat like a forge. Cupric strung a hammock between chimneys, and they took turns swaying above the city, passing a water skin laced with stolen peppermint cordial.
`Could get used to this,' she said, her voice slurred with sleep.
Yiming watched a meteor streak the sky. `To what? Hammocks or heatwaves?'
`To not running.'
The end of summer came not with a bang, but with a slow, golden sigh. Oxford seemed to hold its breath, the city suspended between the languid heat of August and the crisp precision of autumn. The Isis, once glittering under a relentless sun, now flowed heavier, its surface speckled with the first fallen leaves - maple wings of amber and crimson that spun lazily in the eddies. In the garret on Merton Street, the air hummed with the quiet tension of things left unsaid, the walls steeped in the scent of beeswax, solder, and the faintest trace of Russian Caravan tea.
Yiming and Cupric moved through those final days like partners in a silent dance. Mornings began with the samovar's familiar hiss, its brass belly polished to a dull gleam by Cupric's relentless hands. She'd rise first, padding barefoot across the creaking floorboards to kindle the flame, while Yiming lingered in the thin light of dawn, watching her silhouette blur through half-closed eyes. By the time he stumbled to the table, a chipped mug would already await him, steam curling into the honeyed shafts of sunlight that sliced through the curtains.
`Your daft books mention how to brew tea yet?' she'd ask, her voice rough with sleep, as she leant against the hearth.
`Only in Latin,' he'd grumble, thumbing open a journal on alloy conductivity, its margins already littered with her annotations: `Bessemer's a prat - see p. 43' and `Try nickel next time?'
The afternoons sprawled into rituals of their own. Cupric had commandeered a corner of the garret for her repairs - a salvaged clock from Pembroke College, a dented candelabra from a vicarage jumble sale, a music box whose gears she'd coaxed back to a tinny rendition of Greensleeves. Yiming, meanwhile, spread his papers like a siege across the floor, equations and diagrams colonizing every surface. They worked in companionable silence, broken only by the occasional clink of tools or the rustle of pages. Sometimes, she'd toss him a screwdriver mid-sentence; sometimes, he'd read aloud a passage so pompous it warranted her mockery.
```The metallurgical implications of crystalline lattice structures cannot be understated,''' he'd intone, deadpan.
```Cannot be understated,''' she'd parrot, rolling her eyes. `Fancy words for ``shiny rocks''. Pass the pliers.'
Evenings were reserved for the river. They'd escape the garret's clutter for the Cherwell, its banks still warm from the sun. Cupric poled the punt with the ease of someone born to it, her calloused hands gripping the wood as naturally as a hammer. Yiming lounged in the bow, a volume of Keats balanced on his knees, though he rarely read a page. Instead, he watched her - the way her hair frayed from its braid in the humidity, the way her shoulders flexed as she steered them clear of reeds, the way she'd smirk when he trailed his fingers in the water, sending ripples skittering toward the shallows.
One such evening, as the sky bruised into twilight, she let the punt drift beneath a canopy of willows. The air thrummed with the whine of cicadas, the water lapping against the hull like a whispered secret.
`Suppose you'll be too busy for this soon,' she said abruptly, grounding the pole in the mud.
Yiming glanced up. `For what? Floating aimlessly while you do all the work?'
`Aye.' She didn't smile. `Lectures. Libraries. All that\dots' She waved a hand, as if swatting at a fly. `Scholar's nonsense.'
He closed the book. `It's not nonsense.'
`Didn't say it was.' She sat abruptly, the punt rocking. `Just said you'll be busy.'
The unspoken words hung between them, thicker than the humidity. Yiming reached for the pole, his hand brushing hers. `I'll still be here. We'll still be here.'
She snorted, but didn't pull away. `In this leaky coffin?'
`It's not leaking.'
`Only because I patched it.'
He laughed, the sound swallowed by the willow's sigh. `Then I'll rely on your repairs.'
The true end came on a day thick with the scent of rain. The sky hung low and leaden, the air crackling with the promise of a storm. Cupric stood at the garret window, watching undergraduates swarm the streets below like ants, their laughter sharp and foreign after months of quiet.
`They've no idea,' she muttered, her breath fogging the glass.
`About what?' Yiming asked, sorting lecture notes into a battered satchel.
`About any of it.' She turned, her arms crossed. `The furnaces. The strikes. The cost of a loaf in Sheffield when the mills shut down.'
He paused, a pamphlet on Bessemer's legacy half-tucked into his bag. `You could tell them.'
`Aye. And they'd nod and sip their port and forget by dessert.'
The first raindrops struck the pane, slow and fat. Yiming crossed the room, his hand hovering at the small of her back - a question. When she didn't move, he let it settle there, the warmth of her seeping through cotton.
`Doesn't mean we forget,' he said quietly.
She leant into him, just slightly. `Suppose not.'
That night, the storm broke in earnest. Rain lashed the garret's roof, the wind howling through the chimney like a banshee. They huddled by the samovar, its glow painting the walls in flickering bronze. Cupric nursed a mug of spiked cider, her knees drawn to her chest. Yiming pretended to read, though his eyes kept straying to the way the firelight gilded her profile.
`You'll write?' she asked suddenly, her voice barely audible over the rain.
He blinked. `What?'
`When you're off in your labs. Lectures. Whatever.' She stared into her mug. `Or will I just find your notes scrawled on the walls?'
He set the book aside. `I'm not going anywhere.'
`Aye, but they are.' She jerked her chin at the window, where the spire of Christ Church pierced the storm. `All those toffs with their Latin and their laws. They'll swallow you whole.'
`Not if you're here to yank me back.'
She met his gaze then, her eyes reflecting the samovar's flame. `And if I'm not?'
The words hung, dangerous and raw. Yiming reached for her hand, his thumb tracing the ridge of her knuckles - a map of scars and solder burns. `Then I'll find you.'
The storm raged on. Somewhere, a shutter tore loose, clattering into the lane. Cupric's fingers tightened around his.
`Sentimental fool,' she muttered.
`Aye,' he said. `But I'm your fool.'
Morning dawned brittle and clear, the air scrubbed clean by the storm. Yiming's first lecture began at nine. He dressed methodically: waistcoat, watch chain, a cravat knotted with unsteady hands. Cupric watched from the hearth, her boots propped on the samovar's crate.
`You look like a banker,' she said, scowling.
`I look like a scholar.'
`Same difference.'
He adjusted his cuffs, suppressing a smile. `Coming?'
She hesitated, then snatched her coat from the hook. `Someone's got to keep you from tripping on your own laces.'
The streets teemed with students, their chatter bouncing off the ancient stones. Cupric walked a half-step behind, her presence a steady anchor in the chaos. At the lecture hall's steps, Yiming paused, the weight of the moment settling on his shoulders.
`Well?' she prompted, nudging him forward.
He took a breath - then turned, catching her hand. `Stay.'
`What?'
`Stay. Here. With me.' The words tumbled out, unpolished and urgent. `Not just for summer. Always.'
For a heartbeat, the world stilled. Then Cupric's smirk flickered, softer at the edges. `And who'll fix the samovar when it cracks?'
`You will.'
She huffed, but her fingers laced through his. `Sentimental fool.'
`Aye,' he said, tugging her toward the door. `But I'm your fool.'